---
title: "Ass3"
author: "Marcos Bernier"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: yes
    toc_float: yes
    
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## I did 15/16 :(

# Question 1

## A

The time is 2 minutes = 120 seconds. The rate required by the function pexp must be under 1 so instwad of 95, I pass 1/95 to the function

```{r}
1-pexp(120,1/95)
```

## B

```{r}
phish <- read.csv("PHISHING.CSV")
(mean(phish$INTTIME)-95)/95
(var(phish$INTTIME)-9025)/9025


```


The mean and variation indicate that it follows an exponential distribution with 95.

# Question 2

## A

```{r}
a = 3
b = 0.07

3*.07
3*(.07*.07)
```

## B

Max flood is .6 M cft/s but within 3sd of the mean is .57 mil. .6 is an outlier. Not to be expected because it is an outlier. 

# Question 3

## A

$m_a = 2*2 = 4$
$m_b = 1*4 = 4$

## B

$v_a = 2*2^2 = 8$
$v_b = 1*4^2 = 16$

## C

```{r}
pgamma(1,2,1/2)
pgamma(1,1,1/4)
```

A probability is 9 ~ percent. While B is 22 ~ percent. B is much more likely to cause a reaction in <1 min.


# Question 4

## A

Weibull. 

```{r}
pweibull(2,2,2)
```

## B

$2*.88623 = 1.77246$
$4(1-0.88623^2) = .8583$

The mean is 1.77~ and the SD is .9265~.



## C

This can be solved by running

```{r}
pweibull(3.62546,2,2) - pweibull(-0.08054,2,2)
```

The probability is .962

## D

Use R again for P(Y>6)

```{r}
1-pweibull(6,2,2)
```

Very unlikely.

# Question 5

## A

$a=2,b=11$ so $m=2/11 = .18182$ and $v=18/{{11^2(11)}} = 0.01240$

## B

To find the probability 40% of hardware repair will be laser printer, you can use pbeta. P(y>=.4)
```{r}
1-pbeta(.4,2,9)
```

## C

Again, pbeta can be used to find this probability. P(<=.1)

```{r}
pbeta(.1,2,9)
```


# Question 6

## A

The values are respectively 2, and 16

## B

$4*.88623 = 3.54492$
$16(1-.88623^2)=3.4335$

## C

To calculate the probability concerning 6 years failure free use pweibull once more

```{r}
1-pweibull(6,2,4)
```

# Question 7

## A

```{r}
row = c()
for(i in 1:36)
{
  row = c(row,1/36)
}
row
```

## B

$P(X=1) = p_1(1) = 1/36 * 6 = 1/6$
$p_1(X) = 1/6$

$P(Y=1) = p_2(1) = 1/36 * 6 = 1/6$
$p_2(Y) = 1/6$

## C

$p(x,y)/p_2(y)$

$p(1,1) = p(1,1)/p_2(1) = 1/6$


$p(x,y)/p_1(x)$

$p(1,1) = p(1,1)/p_1(1) = 1/6$

The conditional probabilities are the same as the joint probability table.

## D
The occurence of one event does not impact the other event occuring. This implies that they are independent.

# Question 8

## A

```{r}
t1<- c(1/7,2/7,1/7)
t2<- c(0,0,2/7)
t3<- c(0,0, 1/7)
t1
t2
t3
```

## B


```{r}
t1<- c(1/7,2/7,1/7)
t2<- c(0,0,2/7)
t3<- c(0,0, 1/7)
t1
t2
t3
c(t1[1]+t2[1]+t3[1],t1[2]+t2[2]+t3[2],t1[3]+t2[3]+t3[3])
```

## B

```{r}
t1<- c(1/7,2/7,1/7)
t2<- c(0,0,2/7)
t3<- c(0,0, 1/7)
t1 = c(t1,sum(t1[1],t1[2],t1[3]))
t2 = c(t2,sum(t2[1],t2[2],t2[3]))
t3 = c(t3,sum(t3[1],t3[2],t3[3]))

t1
t2
t3


```


## C

```{r}
c(1,1,1/4)
c(0,0,1/2)
c(0,0,1/4)
```


# Question 9

## A

$f_2(y)= \int_y^{2y}f(x,y)dx $
$=== \frac{e^{-y/10}}{10}$

## B

The expected value of a CRV is beta. Beta is 10 so the EV is 10.

# Question 10

## A

${cxe^{-x^2}}/-2x$ from 0 to inf $=1$

so 

$0 - {ce^{-0^2}}/{-2} = 1$
$c/2$ = 1

$c=2$



## B

$f_1(x)=2xe^{-x^2}$

integrate

$2xe^{-x^2}/{-2x}$ from o to inf = 1

$0 - 2e^{-0^2}/{-2}$ = 1



## C

$f_1(x)=1$

$f_2(y|x) = 2e^{-x^2}$

Shown :)

# Question 11

The covariance of X,Y = E(XY) - E(X)E(Y)
E(XY) = 0, and respective expected vaues also = 0. So COV(X,Y) =0. Y is depdndent on X. If x = 2, Y can only be =X or =-X.


# Question 13

## A
$P(Y<=1) = P(Z<-2.9668)$

```{r}
pnorm(-2.9668)
```

## B

$P(Y>=11) = P(Z>1.1410)$

```{r}
1-pnorm(1.1410)
```

## C

```{r}
pbinom(1,20,.4)
1-pbinom(10,20,.4)
```

It provides a good approx.

# Question 14

## A

```{r}
library(readxl)
dird = "/Users/marcosbernier/Dev/stats/MATH4753BERN0021/assignments/ass3"

myread = function(xls){
  require(readxl)
read_xls(paste0(dird, xls))
}
leadcop = myread("/LEADCOPP.xls")
t.test(leadcop$LEAD,conf.level = 0.99)
```

## B

```{r}
t.test(leadcop$COPPER,conf.level = 0.99)

```


## C

99% of lead falls between -1.1478 and 6.919. 99% of copper falls betweem .1518 and .6647.

## D

99% of intervals contain the values.

# Question 15

```{r}
library(readxl)
dird = "/Users/marcosbernier/Dev/stats/MATH4753BERN0021/assignments/ass3"

myread = function(xls){
  require(readxl)
read_xls(paste0(dird, xls))
}
solrad = myread("/SOLARAD.xls")
```

```{r}
with(solrad, t.test(STJOS, IOWA, paired=TRUE, conf.level = 0.95))
```

Between 156.8193 and 239.1807.

# Question 16

## A

```{r}
diazinon = myread("/DIAZINON.xls")
with( diazinon, t.test(DAY, NIGHT, paired =TRUE, conf.level = .90))
```

90% is between -58.8992 and -18.9190

## B

The population has a normal distribution.

## C

The diazon levels do differ between day and night.




