---
title: "Lab2"
author: "Marcos Bernier"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: yes
    toc_float: yes
    
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Tasks

## Task1
```{r}
getwd()
```

## Task2
```{r}
rford <- read.csv("EPAGAS-1.csv")
head(rford)
```

## Task 3
```{r}
ford <- read.csv("DDT.CSV")
mpg <- ford$WEIGHT
z = (mpg - mean(mpg))/sd(mpg)
possible <- mpg[abs(z) > 2 & abs(z) <= 3]
possible



```


## Task 4
```{r}
s <- boxplot(mpg, notch = TRUE, horizontal = TRUE, col = "BLACK", main = "Boxplot for MPG")
```

Chebyshev’s Theorem says 1-1/2^2, or 75% if the data will fall between. The actual answer is:
```{r}
length(mpg[abs(z)<2])/length(mpg)
```

which falls above te "at least" mark set by the theorem, so the theorem agrees with the actual answer.

The empirical rule says that around 95% of the data should fall between 2 standard deviations of the mean. The real answer is
```{r}
length(mpg[abs(z)<2])/length(mpg)
```
There is a one point difference between the actual calculated value and the empirical rule's predicted value. 
```{r}
ss <- density(mpg)
plot(ss)
```

Because the data is roughly bell-shaped, we can apply the empircal rule in this case.



```{r}
curve( 15*x^2, from=2, to=20, n=300, xlab="nvalue", ylab="T(n)value", 
             col="blue", lwd=2, main="Plot of 15n^2"  )
curve( 8*x^3, from=2, to=20, n=300, xlab="nvalue", ylab="T(n)value", 
             col="blue", lwd=2, main="Plot of 8n^3"  )
curve( 2^x, from=2, to=20, n=300, xlab="nvalue", ylab="T(n)value", 
             col="blue", lwd=2, main="Plot of 2^n"  )
curve( 3^x, from=2, to=20, n=300, xlab="nvalue", ylab="T(n)value", 
             col="blue", lwd=2, main="Plot of 3^n"  )
curve( factorial(x), from=2, to=20, n=300, xlab="nvalue", ylab="T(n)value", 
             col="blue", lwd=2, main="Plot of n!"  )
curve( x*log(x), from=2, to=20, n=300, xlab="nvalue", ylab="T(n)value", 
             col="blue", lwd=2, main="Plot of nlog(n)"  )
```



