---
title: "Lab1"
author: "Marcos Bernier"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: yes
    toc_float: yes
    
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Tasks

## Task 1

The working directory

```{r}
getwd()
```

## Task 2

The data

```{r}
ddt <- read.csv("DDT-1.csv")
head(ddt)
```

## Task 3

* The qualitive variables are RIVER, and SPECIES
* The quantitative variables are the LENGTH, MILE, WEIGHT, DDT.
* There are 3 species in the ddt set:
```{r}
table(ddt$SPECIES)
```

* Subset with WEIGHT>800, SPECIES=LMBASS
```{r}
with(ddt, ddt[WEIGHT>800 & SPECIES=="LMBASS",])
```
* Subset with RIVER=SCM and DDT>4.0
```{r}
with(ddt, ddt[DDT>4.0 & RIVER=="SCM",])
```

## Clicker Questions

* The mean length of fish
```{r}
mean(ddt$LENGTH)
```
* The standard dev of weight
```{r}
sd(ddt$WEIGHT)
```

* Yes, thats plot of LENGTH VS WEIGHT

* Answer to v/20 is below:
```{r}
v = 1:20
ans = v/20
ans
```

  

## Task 4

* Table of rivers
```{r}
table(ddt$RIVER)
```
* Barplot of the rivers
```{r}
sp=with(ddt,table(RIVER))
barplot(sp,beside=TRUE,col=1:4)
```

* Table of rivers crossed with SPECIES
```{r}
ss = table(ddt$RIVER,ddt$SPECIES)
head(ss)
```
* Barplot of rivers crossed with fish
```{r}
barplot(ss,beside = TRUE, col=1:4)
```

## Task 5

* Pie chart of fish
```{r}
pie(table(ddt$SPECIES))
```

* Pie chart of rivers
```{r}
pie(table(ddt$RIVER))
```

## Task 6

* Boxplot of DDT
```{r}
layout(matrix(c(1,2,3),nr=1,nc=1))
with(ddt,boxplot(DDT,ylab="DDT",col="Green",notch=TRUE))
```

* Boxplot of WEIGHT
```{r}
layout(matrix(c(1,2,3),nr=1,nc=1))
with(ddt,boxplot(WEIGHT,ylab="WEIGHT",col="Red",notch=TRUE))
```

* Boxplot of LENGTH
```{r}
layout(matrix(c(1,2,3),nr=1,nc=1))# 1 row 3 cols
with(ddt,boxplot(LENGTH,ylab="LENGTH",col="Red",notch=TRUE))
```

## Task 7

* Length vs weight given river
```{r}
rivcol=with(ddt, ifelse(RIVER=="FCM","Red",
                        ifelse(RIVER=="LCM","Blue",
                               ifelse(RIVER=="SCM","Green","Black"))))
coplot(WEIGHT~LENGTH|RIVER,data=ddt,col=rivcol)
```

* DDT vs Weight given Species
```{r}
speccol=with(ddt, ifelse(SPECIES=="LMBASS","Red",
                        ifelse(SPECIES=="SMBUFFALO","Blue",
                               ifelse(SPECIES=="CCATFISH","Green","Black"))))
coplot(WEIGHT~DDT|SPECIES,data=ddt,col=speccol)
```

## Task 8

* First
```{r}
library(ggplot2)
g <- ggplot(ddt, aes(x = SPECIES, y = WEIGHT ))
g = g + geom_boxplot(aes(fill = RIVER)) + labs(title = "Marcos Bernier")
g
```

* Second
```{r}
library(ggplot2)
g <- ggplot(ddt, aes(x = RIVER, y = LENGTH ))
g = g + geom_violin(aes(fill = SPECIES)) + labs(title = "Marcos Bernier")
g
```

* Third
```{r}
library(ggplot2)
g <- ggplot(ddt, aes(x = WEIGHT, y = LENGTH ))
g = g + labs(title = "Marcos Bernier") + geom_point(aes(col = SPECIES))
g
```

