---
title: "Ass4"
author: "Marcos Bernier"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: yes
    toc_float: yes
    
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# 10/10 done



# QUESTION 1

## a

```{r}

mydata <- read.csv("NZBIRDS.csv")
samples <- sample(1:133, 35)
sample = mydata[samples,]
sample

```

## b

```{r}
mp <- c(-1,1)
mean(sample$Body.Mass) + mp*qt(1-.05,34)*sd(sample$Body.Mass)/sqrt(35)
```


## c

95% of means of body masses of birds will fall into the interval.

## d

The interval has 95% confidence, it will most likely contain mu.

## e

```{r}
mean(sample$Egg.Length) + mp*qt(1-.05,34)*sd(sample$Egg.Length)/sqrt(35)
```


## f

```{r}
n1 = 38 
n2 = 78 

p1hat = 21 / n1  
q1hat = 1 - p1hat
p2hat = 7 / n2
q2hat = 1 - p2hat

mp = c(-1,1)
ci <- (p1hat - p2hat) + mp * qnorm(1-.05/2,0,1)*sqrt((p1hat*q1hat/n1) + (p2hat*q2hat/n2))
ci
```


## g

Yes

# QUESTION 2

```{r}
t.test(rnorm(100,mean=1312,sd=422),rnorm(47,mean=1352,sd=271),conf.level = .95)
```


# QUESTION 3

## a

$y \sim N(0,\sigma^2)$

$z = y/{\sigma} \sim N(0,1)$

g(v) = GPRIME(v) = $1/\sqrt pi \sqrt 2 ^{v^{1/2 -1 e -v/2 dy}}$


## b

( $ y^2/{\lambda^2 0.0025,1} $ , $ y^2/{\lambda^2 0.0975,1} $ )


# QUESTION 4

## a

$\mu = 2$

$\mu      != 2$

## b

T: -1.02 P: 0.322


## c

$|T| < 2.1262$

## d

P > alpha so the null hypothesis can be accepted as true.


## e

They can both use the null hypthesis against the alternative hypothesis.


# QUESTION 5

## a

The sample size is 25. The mean of the population is 15. The mean of thew sample is 14.516. The SD of the sameple is 12.9637.  

H0: mu = 15, h1 is opposite

(xbar - mu)/S/sqrt(n) = -0.1867

alpha = .1, then p = .854
The sample is representative of all Wisconsin lakes

## b

The mean is 14. There is no significant difference.

# QUESTION 6

```{r}
q6 <- read.csv("ORCHARD.csv")

t.test(q6$CONDITION == "FOG",q6$CONDITION != "FOG",mu = 0, conf.level = .95)
```


# QUESTION 7

## a 

```{r}

turbine <- read.csv("GASTURBINE.csv")



var.test(turbine[turbine$ENGINE == "Traditional",]$HEATRATE,turbine[turbine$ENGINE == "Aeroderiv",]$HEATRATE, conf.level = .95 )
```


## b

```{r}
var.test(turbine[turbine$ENGINE=="Advanced",]$HEATRATE,turbine[turbine$ENGINE == "Aeroderiv",]$HEATRATE,conf.level = .95, var.equal=T)
```


# QUESTION 8


## a

For h0 there is no significant differences between the variances at each site.

H0 = sigma^2 = sigma2^2 

For h1 there is a significant difference between both site variances.

H1 = opposite of null

## b

```{r}
gob = read.csv("GOBIANTS.csv")

head(gob)
```

F=S21/S22 so
F=1.0498

## c

The rejection region is where
$F > F_{\alpha/2}$,  
$F_{\alpha/2}$ being where x numerator and $x_2$ are the degrees of freedom for the numerator and denominator sample variances.

Since alpha is .5, alpha/2 is .025. 

$F_{0.025} (25.25) = 2.23$ so $H_0$ is rejected when F exceeds 2.23.


## d

F was found to be 1.0498.

So the P value 

$P(F<1.0498) = .55$

$P(F>= 1.0498) = 1 -.55 = .45$

$ P = 2 *.45 = .9 $

## e

.05 is less than the P value of .9. This is not in the rejection region so we cannot reject the hypothesis. With 95% confidence we can say there is no significant difference between two variances at the sites.

## f

The P value needs to be less than .05 for this to be true.

# QUESTION 9

The Null hypthesis is $\mu = 0$ and alternative is !=0

```{r}
data<- read.csv("THRUPUT.csv")

t.test(data$HUMAN, data$AUTO, mu=0, paired = T)
```




# QUESTION 10

```{r}
## sample function
set.seed(35) # This will give everyone the same sample
sam=round(rnorm(30,mean=20,sd=3),3)



########### bootstrap function ##################

myboot<-function(iter=10000,x,fun="mean",alpha=0.05,...){  #Notice where the ... is repeated in the code
n=length(x)   #sample size

y=sample(x,n*iter,replace=TRUE)
rs.mat=matrix(y,nr=n,nc=iter,byrow=TRUE)
xstat=apply(rs.mat,2,fun) # xstat is a vector and will have iter values in it 
ci=quantile(xstat,c(alpha/2,1-alpha/2))# Nice way to form a confidence interval
# A histogram follows
# The object para will contain the parameters used to make the histogram
para=hist(xstat,freq=FALSE,las=1,
main=paste("Histogram of Bootstrap sample statistics","\n","alpha=",alpha," iter=",iter,sep=""),
...,col = rainbow(5))

#mat will be a matrix that contains the data, this is done so that I can use apply()
mat=matrix(x,nr=length(x),nc=1,byrow=TRUE)

#pte is the point estimate
#This uses whatever fun is
pte=apply(mat,2,fun)
abline(v=pte,lwd=3,col="Black")# Vertical line
segments(ci[1],0,ci[2],0,lwd=4)      #Make the segment for the ci
text(ci[1],0,paste("(",round(ci[1],2),sep=""),col="Red",cex=3)
text(ci[2],0,paste(round(ci[2],2),")",sep=""),col="Red",cex=3)

# plot the point estimate 1/2 way up the density
text(pte,max(para$density)/2,round(pte,2),cex=3)

return(list(ci=ci,fun=fun,x=x, t=t))# Some output to use if necessary
}
myboot(x=sam)
```

