---
title: 'Ass 2: Template'
author: "Marcos Bernier"
date: '`r format(Sys.Date(),format="%A, %B %d, %Y")`'
output: 
  html_document:
    df_print: paged
    fig_caption: true
    highlights: pygments
    number_sections: no
    theme: spacelab
    toc: yes
    toc_float: yes
---

COMPLETED 16/17

```{r setup, include=FALSE, fig.align='center'}
knitr::opts_chunk$set(echo = TRUE)
```

# Questions{}

## Q 1

a. Because the probability of a correct match is 92.12. The probabolity of not identifying correctly is 7.88%.

b. The probabolity of a correct match is 74.55. So the probabolity of the opposite is 25.45%.

c. The participant is more likely to be a novice.

## Q 2


a. The probability is 50%. $(50/1000) / (100/1000)$

b. 99% $(891/1000)/(900/1000)$

c. $(.1*.5)/((.1*.5)+((.9*.01)))$


## Q 3

Total possible outcomes between two sets is the length of the sets multipled by eachother.

Set X is length 3.
Set Y is length 5.

Total Possible outcomes = $ |X| * |Y| = 3 * 5 = 15$
## Q 4

Let X equal a set of length 4. We want permutation of 3 from the set.

The amount of perm =

$4!/{4-3} = 24/1 = 24 $


## Q 5
X is a set of N elements to be separated into y sets.
$ N!/{n_1! .. n_y!}$

## Q 6

n items are picked - x items are not. x is N-n for N being the size of the pool.

$N!/{n!*{N-n}!}$


## Q 7

a. .3+.37+.09+.2+.04

b. .2 +.04 = .24 ?

c. .09 + .3 = .39

## Q 8

a. 0<=p(y) <=1 is met. all p(y) fit. The sum of all p's = 1. 

b. $.02 + .02 + .02 + .01 +.01+.01+.01+.01+.005+.005$

c. 
```{r}
variance <- round(sum((seq(0,20) - sum(seq(0,20)*c(.17,.10,.11,.11,.10,.10,.07,.05,.03,.02,.02,.02,.02,.02,.01,.01,.01,.01,.01,.005,.005)))^2 * c(.17,.10,.11,.11,.10,.10,.07,.05,.03,.02,.02,.02,.02,.02,.01,.01,.01,.01,.01,.005,.005)),4)

variance
```

d.


```{r}
sqrt(variance)

sum(seq(0,20)*c(.17,.10,.11,.11,.10,.10,.07,.05,.03,.02,.02,.02,.02,.02,.01,.01,.01,.01,.01,.005,.005)) -2*sqrt(variance)

sum(seq(0,20)*c(.17,.10,.11,.11,.10,.10,.07,.05,.03,.02,.02,.02,.02,.02,.01,.01,.01,.01,.01,.005,.005)) +2*sqrt(variance)
```

## Q 9

a. $dbinom(10, 25, .7)$ = .0013

b. $pbinom(5,25,.7)$ = .000000345744

c. $25(.7) = 17.5 = mu$
    $25(.7)(.3) = 5.25 = sigma^2$
    $sigma = sqrt(sigma^2) = 2.2913$
    
d. The out of 25 students, 17.5 on average will have earned a PHD. The std is 2.2913.
 
## Q 10

a. N = 50 and prob = .1

$50!/((5!)^{10}) * .1^{50} = 0.0000005$

b. $.0338 = p(y=0) + p(y = 1)$

## Q 11

a. $p(y) = p*q^{y-1}$

b. $1/{.4} = 2.5 = 1/p$

c. $ p(y) = .4/.6^{0} = 0.4$

d. $ p(y=2) $

## Q 12

a. $ {nr}/N = 80/209 = .3828 $

b. $ {\binom{8}{4}*\binom{201}{6} }/ \binom{209}{10}$ = 0.00017

## Q 13

a. $sigma^{2} = .03$

b. The events need to occur in a specific unit of time,

c. $ y= {.03^{0} * e^{-.03}}/{0!} = .9704$

## Q 14

a. $2c -yc$ $\int_0^1 f(y)dy=1$
$ c = 2/3$

b.  The CDF is .1 Because it is the integral of y aka
$ \int_{-\infty}^{yf(x)dx} $

c. $2/3 * (2*(.4)) - .4^{2}/{2}$ = .48

d. $2/3 * (2(.6) - .6^{2}/2) - 2/3 (2(.1) - .1^2/2) $ = 0.55

## Q 15

a.

b.

c.


## Q 16

a.
```{r}
1-pnorm(-1.5625,0,1)
```
  

b.

```{r}
pnorm(1.5625,0,1)
```


c.

```{r}
pnorm((2)/3.2,mean=0,sd=1) - pnorm(1/3.2,0,1)
```

## Q 17

a. 

```{r}
pnorm(700,605,185)-pnorm(500,605,185)
```

b.

```{r}
pnorm(500,605,185)-pnorm(400,605,185)

```

c.

```{r}
pnorm(850,605,185)
```


d.

```{r}
1-pnorm(1000,605,185)
```

e. 

```{r}
185*(605 + qnorm(.9,0,1))
```
